Selective electroporation of the viral envelope

### 2021-04-04 documents/pure_electroporation.tex
differential

\title{Selective electroporation of the viral envelope}
\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216} \footnote{therobotist@gmail.com, Ontario, Canada.}}}
\date{\small{March 21 2021}}

@@

As a followup to a technical report \cite{notes2021} on inducing

@@

There, the relevant time constants referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to ion diffusion and capacitive charging.

There the relevant damage quantities were mechanical displacement and membrane stress; here we consider transmembrane voltage and pore diameter.

@@

>>>>

\title{Selective electroporation of the viral envelope}
\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{therobotist@gmail.com, Ontario, Canada.}}
\date{\small{March 21 2021}}

@@

\lettrine{A}{s} a followup to a technical report \cite{notes2021}, presenting experimental data on protein capsid adjacent technique;

There, the relevant time constants referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to ion diffusion and capacitive charging. The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.

@@

@@

ultracrepidarian

on the other hand, the idea of shocking a virus is so basic that it can scarcely be believed
